\chapter{First Chapter}
The following project embodies my vision for the database of the comic retailer excelsior. The comic book industry relies on physical items, which have so far mostly been displayed on physical storefronts and sold in stores. The tradition and history of this domain must be adapted modern demands, in example online retailing. The heart of each online retailer is its underlying database system, which determines how the sold goods are being viewed, which aspects are emphasized and how all parts of the business come together. The main technical part of my vision is being as close to reality as possible when making design and implementation choices. The project should be lean, yet complex enough to consider the peculiarities and subtleties of comic collecting and selling so that every comic enthusiast would be satisfied with this design. Furthermore, the database should meet all technical criteria to be performant, non-redundant and scalable.
Comic books have become far more than simple entertainment products, which get read once and forgotten afterwards. Comic books have turned into collectables which carry both emotional and financial value. There are single very valuable pieces which got produced only a few times many years ago and even fewer which survived until today. At the same time there are many editions produces and sold today in large quantities. The difficult job of a comic retailer is to satisfy all these different target groups with their different needs and demands. Numerous traits are shared by all comics. These can be differentiated on the abstract level of a comic book batch and the level of each physical copy. On the abstract level, each comic book has a title, publisher, release date and so on. Each physical copy has a condition, which is rated by a uniform evaluation system, a buying and selling price, etc.. The customer must be provided with all relevant information so that he can make an educated buying decision and is satisfied in the long term. The intended application of the project is therefore providing a database which stores all information of the comic books the retailer excelsior sells on which a website can be built.
From a technical perspective, the different abstractions of the data have to be considered when designing the database. It can be expected that the 	stress on the database will be low at the beginning but may grow over time, but it’s not to be expected to enter the domain of big data. The database stores so far only textual information, meaning no pictures or videos. There won’t be an ingoing stream of telemetry data for example which fills up our database. Still, the database must be able to handle increasing traffic through website visitors and deliver results in a short time to provide a satisfying user experience.
The scope of this project is providing a useful solution for dealing with all the data concerning the stock of excelsior. This means keeping track of the current inventory of comics and providing the additional information an enthusiast needs. This additional information to what series a single comic issue belongs, who published this series, which character appears in a comic book and who worked on a comic book. Also, all above-mentioned relevant information of a single copy must be stored, such as the buying price, the selling price, the condition and the format, meaning the cover size and material. On top of that, the database should keep track of all customer information such as the name, date of birth and address. These two parts must be brought together to keep track of inventory changes to document previous purchases. The basis for two more functions on possible the way of a customer to buying a comic book should be provided with database foundations, a wishlist and a shopping cart. Most customers are familiar with such functionalities from other online retailers and may therefore miss those in the online shop of excelsior if absent. Not part of the scope of this project is keeping track of logistic business information such as the physical storage of comics, the buying process of comics before they appear in our inventory and the shipping process. Also, no information regarding the payment except the prices should be stored.

